Avoidance in permutations

### 2014-11-07 project2/paper/paper.tex
small edits to Theorem 28

Note by Lemma \ref{tn_avoidance} that if $x, y, z$ is a subsequence of three elements of a permutation in $T_n$ in the relative order $312$ or $321$, then both $y$ and $z$ must be even.

We now prove that there exists a bijection between the sets $A$ and $B$.

>>>>

Let $a$ be an arbitrary permutation in $A$, and $b$ an arbitrary permutation in $B$. By the definition of $A$, $a$ avoids 312. Pick any positive integer $i\leq n$. We note that all even integers to the right of $i$ and less than $i$ in $a$ must be in decreasing order; otherwise, we would obtain a subsequence with pattern 312. Similarly, all even integers to the right of $i$ and less than $i$ in $b$ must be in increasing order.
